FlowFPX: Nimble Tools for Debugging Floating-Point Exceptions

### 2023-06-02 paper.tex
cleanup

@@

We searched GitHub for open issues in Julia libraries involving difficult-to-find NaNs.
In our first batch of issues, we found the ``RxInfer.jl'' library with an issue\footnote{\url{https://github.com/biaslab/RxInfer.jl/issues/116}} revolving around NaN detection.
We offered our tool for the package authors to use, and within a day the authors were able to track down the location of a NaN and fix the issue---all with minimal guidance.

@@

We would also like to thank the developers of RxInfer.jl for providing us with feedback on how we could make our tools more useful.

>>>>

\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\FlowFPX}{FlowFPX}

@@

We searched GitHub for open issues in Julia libraries involving difficult-to-find NaNs.
In our first batch of issues, we found the \code{RxInfer.jl} library with an issue revolving around NaN detection.\footnote{\url{https://github.com/biaslab/RxInfer.jl/issues/116}}
We offered our tool for the package authors to use, and within a day the authors were able to track down the location of a NaN and fix the issue---all with minimal guidance.

@@

We would also like to thank the developers of \code{RxInfer.jl} for feedback on \FlowFPX{}.
